Variance in scarid grazing behavior across Caribbean reef sites

### 2019-04-23 r/Ch2 outline_V3.Rmd

# summing by site, species, and phase
sum_ssp_vg <- sum_id_vg %>% 
  group_by(site, ta_canopy, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    vg_mean=mean(vg),
    vg_se=sd(vg)/sqrt(n),
    vg_capped_mean=mean(vg_capped),
    vg_capped_se=sd(vg_capped)/sqrt(n),
    fr_mean=mean(fr)
    ) %>% 
  select(-n)

vg_facet <- ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    scale_fill_brewer(palette = "Blues") +
    labs(title="Mean grazing impact by volume (initial phase)", 
         y="Grazing impact (cm3/hr)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.title = element_blank())

@@

grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))
```

>>>>

# summing by site, species, and phase
sum_ssp_vg <- sum_id_vg %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, ta_canopy, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    vg_mean=mean(vg),
    vg_se=sd(vg)/sqrt(n),
    vg_capped_mean=mean(vg_capped),
    vg_capped_se=sd(vg_capped)/sqrt(n),
    fr_mean=mean(fr)
    ) %>% 
  select(-n)

# keep this to get legend for panel
vg_facet <- ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    scale_fill_brewer(palette = "Blues") +
    labs(title="Mean grazing impact by volume (initial phase)", 
         y="Grazing impact (cm3/hr)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.title = element_blank())

@@

grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

g <- grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

ggsave(here("figs/bc_bar_panel.png"),g)
```

```{r}
# geom_point version
# keep this to get legend for panel
vg_facet <- ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_point(stat = "identity", aes(color = fr_mean, size = ta_canopy), position = "dodge") +
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    labs(title="Mean grazing impact by volume (initial phase)", 
         y="Grazing impact (cm3/hr)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 45, hjust = 1)
          )

vg_qup <- ggplot(filter(sum_ssp_vg, species_code == "qup" & phase == "i"), 
                 aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_point(stat = "identity", aes(color = fr_mean, size = ta_canopy), position = "dodge") +
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
  labs(y = expression('Grazing impact (cm'^3*'/hr)'), 
       x = "", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.margin = margin(1, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "italic")
        )

vg_stop <- ggplot(filter(sum_ssp_vg, species_code == "stop" & phase == "i"), 
                  aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_point(stat = "identity", aes(color = fr_mean, size = ta_canopy), position = "dodge") +    
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
  labs(y = "",
       x = "", 
       title = "S. viride") +
  theme_bw() + 
  theme(plot.margin = margin(1, 1, 0, 0, unit = "pt"),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "italic")
        )

grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

g <- grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

ggsave(here("figs/bc_point_panel.png"),g)
```
